---
title: "Graded assignment1"
author: "Yannick Gijrath, 2001202"
output: html_notebook
---

# Packages

We need the package `tidyverse` 

```{r}
library(tidyverse) 
```

# Assignment 1

First, we generate some random data:

```{r}
df1 <- as.data.frame(matrix(runif(20*2), ncol=20) )
head(df1)
```

_df1_ is a wide dataframe. The goal of the assignment is to change _df1_ into a long dataframe _df2_. And show the first rows of the dataframe using `head(df2)`

The dataframe _df2_ should look like this:

| Key | Value      |
|-----|------------|
| V1  | 0.09413864 |
| V1  | 0.69782526 |
| V2  | 0.23460454 |
| V2  | 0.51520514 |
| V3  | 0.63181844 |
| V3  | 0.22807211 |

```{r}
df2 <- gather(df1)
  

head(df2)
```

## Assignment 2

We will generate some data:

```{r}
df3 <- as.data.frame(read.table(header = TRUE, text = '
      id        V_1       V_2                
          1  42.467573  -87.810047     
          2  42.049148  -88.273029
          3  39.110539  -90.324080
                       '))
head(df3)

```


```{r}
df4 <- as.data.frame(read.table(header = TRUE, text = '
     V_3            V_4         id                 
      one         1h            1
      two         1h            1
      three       8h            2
      four        1h            4
'))

head(df4)
```


You will have to merge these files, returning all rows and all columns from both _df3_ and _df5_. Where there are not matching values, return _NA_ for the missings. 

This should be the end result:

| id | V_1      | V_2       | V_3   | V_4 |
|----|----------|-----------|-------|-----|
| 1  | 42.46757 | -87.81005 | one   | 1h  |
| 1  | 42.46757 | -87.81005 | two   | 1h  |
| 2  | 42.04915 | -88.27303 | three | 8h  |
| 3  | 39.11054 | -90.32408 | NA    | NA  |
| 4  | NA       | NA        | four  | 1h  |



```{r}
df5 <- merge(df3, df4, all="true")
df5
```
